%%%%% 0 %%%%%
Mark the correct/incorrect assertions about pointers.

%%% 3 3784-4-2; 3798-4-3; 3805-4-1;  %%%
+ A pointer denotes the location of a value in the memory.

%%% 3 3749-1-0; 3784-4-0; 3798-4-0;  %%%
+ When passing an array to a function, only the starting address is passed.

%%% 4 3749-1-1; 3784-4-1; 3798-4-1; 3805-4-0;  %%%
+ Pointer arithmetic means to add an integer offset to an array pointer.

%%% 4 3749-1-3; 3784-4-3; 3798-4-2; 3805-4-3;  %%%
- The value of a pointer must be an address in the heap memory.

%%% 2 3749-1-2; 3805-4-2;  %%%
- If \verb|p| and \verb|q| are pointers to integers, then \verb|p + q| is a correct expression.

%%%%% 1 %%%%%
We have the following variable definitions:
 \vspace{-3mm}\begin{verbatim}
int p = 2;
int* ptr1;
int* ptr2 = new int(1);
 \end{verbatim}\vspace{-6mm}
Mark the correct/incorrect assignment statements.

%%% 1 3791-1-2;  %%%
+ \verb|ptr1 = ptr2;|

%%% 2 3756-2-3; 3805-1-3;  %%%
- \verb|ptr1 = *ptr2;|

%%% 1 3777-3-2;  %%%
- \verb|ptr1 = *p;|

%%% 3 3749-5-0; 3777-3-0; 3791-1-0;  %%%
- \verb|ptr1 = p;|

%%% 3 3770-5-2; 3777-3-3; 3798-1-1;  %%%
+ \verb|ptr1 = NULL;|

%%% 1 3756-2-0;  %%%
- \verb|ptr1 = 20;|

%%% 2 3749-5-1; 3784-2-1;  %%%
- \verb|*ptr1 = ptr2;|

%%% 1 3812-5-0;  %%%
+ \verb|*ptr1 = *ptr2;|

%%% 1 3784-2-2;  %%%
- \verb|*ptr1 = *p;|

%%% 1 3812-5-1;  %%%
+ \verb|*ptr1 = p;|

%%% 3 3770-5-1; 3805-1-0; 3812-5-3;  %%%
- \verb|*ptr1 = NULL;|

%%% 1 3749-5-2;  %%%
+ \verb|*ptr1 = 20;|

%%% 4 3749-5-3; 3756-2-1; 3791-1-3; 3798-1-0;  %%%
+ \verb|p = *ptr2;|

%%% 2 3756-2-2; 3784-2-0;  %%%
- \verb|p = ptr2;|

%%% 2 3805-1-1; 3812-5-2;  %%%
+ \verb|p = 20;|

%%% 1 3791-1-1;  %%%
- \verb|*p = *ptr2;|

%%% 2 3798-1-2; 3805-1-2;  %%%
- \verb|*p = ptr2;|

%%% 3 3770-5-3; 3777-3-1; 3784-2-3;  %%%
- \verb|*p = NULL;|

%%% 2 3770-5-0; 3798-1-3;  %%%
- \verb|*p = 20;|

%%%%% 2 %%%%%
We have the following variable definitions:
 \vspace{-3mm}\begin{verbatim}
int a[3] = {1, 2, 3};
int* pa = a;
 \end{verbatim}\vspace{-6mm}
Mark with ``yes'' expressions which have value 3.

%%% 5 3770-4-2; 3791-5-0; 3798-5-2; 3805-2-2; 3812-4-1;  %%%
+ \verb|a[0] + a[1]|

%%% 2 3763-5-3; 3770-4-0;  %%%
+ \verb|a[0] + pa[1]|

%%% 2 3749-3-0; 3770-4-3;  %%%
+ \verb|(*pa) + a[1]|

%%% 5 3749-3-3; 3770-4-1; 3777-1-1; 3791-5-1; 3798-5-3;  %%%
+ \verb|(*pa) * 3|

%%% 5 3749-3-2; 3763-5-1; 3777-1-2; 3791-5-3; 3805-2-3;  %%%
+ \verb|*(pa + 2)|

%%% 4 3763-5-0; 3777-1-3; 3805-2-0; 3812-4-2;  %%%
- \verb|*pa + *a|

%%% 1 3805-2-1;  %%%
- \verb|pa[0] + a[0]|

%%% 6 3749-3-1; 3763-5-2; 3777-1-0; 3791-5-2; 3798-5-1; 3812-4-0;  %%%
- \verb|pa[1] + a[1]|

%%% 2 3798-5-0; 3812-4-3;  %%%
+ \verb|3*(*pa)|

%%%%% 3 %%%%%
Mark the correct/incorrect definitions and initializations 
of character pointers and arrays.

%%% 2 3749-2-2; 3763-2-3;  %%%
+ \verb|char hello[] = "Hello";|

%%% 2 3770-2-3; 3777-4-2;  %%%
+ \verb|char* p = "pointer";|

%%% 0  %%%
+ \verb|char* year = "2014";|

%%% 4 3749-2-0; 3763-2-1; 3770-2-0; 3777-4-3;  %%%
+ \verb|char* heap = new char;|

%%% 0  %%%
+ \verb|char car[10] = "Volvo";|

%%% 0  %%%
+ \verb|char miles[] = "1000";|

%%% 2 3770-2-1; 3777-4-0;  %%%
+ \verb|char just[5] = "just";|

%%% 3 3749-2-3; 3770-2-2; 3777-4-1;  %%%
- \verb|char bye[7] = "bye-bye";|

%%% 1 3749-2-1;  %%%
- \verb|char one[1] = "1";|

%%% 0  %%%
- \verb|char* hit = -1;|

%%% 1 3763-2-0;  %%%
- \verb|char* oops = {0};|

%%% 1 3763-2-2;  %%%
- \verb|char hey[] = 1;|

%%%%% 4 %%%%%
We have the following classes:
 \vspace{-3mm}\begin{verbatim}
class Point {
... };
class Circle : public Point {
... };
 \end{verbatim}\vspace{-6mm}
Mark the correct/incorrect assertions about the classes
\verb|Point| and \verb|Circle|.

%%% 4 3749-4-1; 3777-2-3; 3798-2-2; 3805-3-0;  %%%
+ The class \verb|Point| is the base class and the class \verb|Circle| is the derived class.

%%% 6 3756-3-0; 3763-4-1; 3770-1-2; 3777-2-0; 3791-3-0; 3798-2-1;  %%%
- The class \verb|Circle| is the base class and the class \verb|Point| is the derived class.

%%% 4 3756-3-2; 3763-4-0; 3791-3-1; 3812-2-2;  %%%
+ The data members of the class \verb|Point| are present in each object of the class \verb|Circle|.

%%% 5 3749-4-2; 3756-3-3; 3763-4-2; 3798-2-3; 3812-2-1;  %%%
- The data members of the class \verb|Circle| are present in each object of the class \verb|Point|.

%%% 8 3749-4-3; 3763-4-3; 3770-1-0; 3777-2-2; 3791-3-2; 3798-2-0; 3805-3-1; 3812-2-0;  %%%
- The member functions of the class \verb|Circle| have access to any data member of the class \verb|Point|.

%%% 3 3770-1-1; 3777-2-1; 3805-3-3;  %%%
- The member functions of the class \verb|Point| have access to any data member of the class \verb|Circle|.

%%% 6 3749-4-0; 3756-3-1; 3770-1-3; 3791-3-3; 3805-3-2; 3812-2-3;  %%%
+ The member functions of the class \verb|Circle| have access to any public member function of the class \verb|Point|.

%%%%% 5 %%%%%
Suppose the class \verb|D| inherits from \verb|B|. Let
\verb|b| be an object of the class \verb|B|,
\verb|d| be an object of the class \verb|D|,
\verb|pb| be a pointer of the class \verb|B| and
\verb|pd| be a pointer of the class \verb|D|.
Which of the following assignments are legal?

%%% 0  %%%
+ \verb|b = d;|

%%% 1 3756-5-0;  %%%
- \verb|d = b;|

%%% 0  %%%
- \verb|pd = pb;|

%%% 3 3756-5-3; 3770-3-1; 3784-5-1;  %%%
+ \verb|pb = pd;|

%%% 0  %%%
+ \verb|*pb = *pd;|

%%% 2 3756-5-2; 3770-3-0;  %%%
- \verb|*pd = *pb;|

%%% 1 3784-5-0;  %%%
+ \verb|b = *pd;|

%%% 0  %%%
+ \verb|b = *pb;|

%%% 3 3756-5-1; 3770-3-2; 3784-5-2;  %%%
+ \verb|d = *pd;|

%%% 0  %%%
- \verb|d = *pb;|

%%% 0  %%%
+ \verb|*pd = b;|

%%% 1 3784-5-3;  %%%
+ \verb|*pb = b;|

%%% 0  %%%
+ \verb|*pd = d;|

%%% 1 3770-3-3;  %%%
- \verb|*pb = d;|

%%%%% 6 %%%%%
Mark the correct/incorrect assertions about inheritance
hierarchy of stream classes.

%%% 4 3777-5-0; 3784-3-1; 3791-2-2; 3812-1-3;  %%%
+ The \verb|fstream| class derives from \verb|iostream|.

%%% 2 3763-1-0; 3798-3-1;  %%%
- The \verb|fstream| class derives from \verb|ofstream|.

%%% 5 3756-1-2; 3777-5-3; 3791-2-0; 3798-3-0; 3812-1-2;  %%%
- The \verb|fstream| class derives from \verb|ifstream|.

%%% 2 3763-1-2; 3777-5-2;  %%%
+ The \verb|iostream| class derives from \verb|istream| and \verb|ostream|.

%%% 4 3756-1-3; 3777-5-1; 3784-3-2; 3798-3-3;  %%%
+ The \verb|ifstream| class derives from \verb|istream|.

%%% 3 3756-1-0; 3791-2-1; 3812-1-1;  %%%
+ The \verb|ostringstream| class derives from \verb|ostream|.

%%% 4 3784-3-0; 3791-2-3; 3798-3-2; 3812-1-0;  %%%
+ The \verb|istringstream| class derives from \verb|istream|.

%%% 2 3756-1-1; 3763-1-1;  %%%
- The \verb|iostream| class derives from \verb|ifstream| and \verb|ofstream|.

%%% 2 3763-1-3; 3784-3-3;  %%%
- The \verb|fstream| class derives from \verb|ifstream| and \verb|ofstream|.

%%%%% 7 %%%%%
Mark the correct/incorrect assertions about stream classes, objects and
member functions.

%%% 1 3784-1-2;  %%%
+ An object of \verb|istream| class is a source of bytes.

%%% 1 3763-3-2;  %%%
+ An object of \verb|ostream| class is a destination for bytes.

%%% 0  %%%
+ The \verb|get| member-function is defined for \verb|istream| objects.

%%% 2 3756-4-0; 3812-3-1;  %%%
+ The \verb|getline| member-function is defined for \verb|istream| objects.

%%% 1 3805-5-3;  %%%
+ The \verb|>>| operator is defined for \verb|istream| objects.

%%% 2 3756-4-2; 3805-5-2;  %%%
+ The \verb|<<| operator is defined for \verb|ostream| objects.

%%% 3 3763-3-1; 3791-4-0; 3805-5-0;  %%%
+ The object \verb|cin| belongs to a class that is derived from \verb|istream|.

%%% 3 3756-4-1; 3791-4-1; 3805-5-1;  %%%
- The object \verb|cin| belongs to a class that is derived from \verb|ifstream|.

%%% 3 3784-1-3; 3791-4-3; 3812-3-0;  %%%
+ The object \verb|cout| belongs to a class that is derived from \verb|ostream|.

%%% 0  %%%
- The object \verb|cout| belongs to a class that is derived from \verb|ofstream|.

%%% 2 3763-3-3; 3791-4-2;  %%%
- The \verb|open| member-function is defined for \verb|istream| objects.

%%% 2 3756-4-3; 3784-1-0;  %%%
+ The \verb|close| member-function is defined for \verb|fstream| objects.

%%% 1 3812-3-3;  %%%
- The object \verb|cin| belongs to the class \verb|iostream|.

%%% 3 3763-3-0; 3784-1-1; 3812-3-2;  %%%
- The object \verb|cout| belongs to the class \verb|iostream|.

